Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2017-01-10 draft.tex
Minor edits to decay section.

As we mentioned above, we find SN1987A constraints on dark photon SIDM models that are considerably different 
from those of \cite{dent_etal12}. If correct, this has important consequences. The Snowmass white paper by Kaplinghat, 
Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely summarizes a variety of constraints on dark electromagnetism models of 
SIDM. One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there is only a narrow range of 
viable photon mixing parameters that can lead to production of SIDM in the early universe, while evading all constraints, 
including the constraint of \cite{dent_etal12}. Our results suggest that the SN1987A constraints from Ref.~\cite{dent_etal12} 
are too restrictive. The less restrictive constraints that we quote open up a space of unrestricted mixing parameters that 
ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated constraints corresponds to a 
space that may a significant impact on cosmological structure formation, particularly the structures of dark matter halos and galaxies.

The discrepancy between our result and that of Ref.~\cite{dent_etal12} is due to several factors. First, it is straightforward to 
demonstrate that the kinematical relationships in given in Appendix A of Ref.~\cite{dent_etal12} are incorrect. Second, the 
squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} are incorrect. Our squared matrix elements 
are considerably more complicated. There appear to be a number of errors that led to the incorrect squared matrix elements in 
Ref.~\cite{dent_etal12}. At the very least, these errors include simplification using the incorrect kinematics and neglect of the 
mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). Additional 
discrepancies must be present, the causes of which are not apparent from the exposition, 
because the squared matrix elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} 
do not obey the correct symmetries under interchange of the incoming or outgoing baryon momenta. 
Given these errors, we suggest that our results should supercede these previously-published constraints.

@@

\subsection{Bremsstrahlung amplitude calculation}

@@

\arz{Cameron, can you double check this. I think there were some errors in the momenta and in the relative 
signs of the diagrams. I tried to fixe them.}
The eight diagrams contribute the following eight terms to the pp amplitude, 
%
\begin{widetext}
\begin{eqnarray}
	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1} 
	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2} 
	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
	\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3} 
	\bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
	\bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4} 
	\bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
\end{eqnarray}
\end{widetext}
%
where the dark photon polarization is given by $\epsilon$. The squared amplitude is given by 
%
\begin{equation}
\vert \mathcal{M}_{\mathrm{pp}} \vert^2 = \sum_{s_1,s_2}\, \left\vert \sum_{i=1}^{8}\, M_i \right\vert^2, 
\end{equation}
%
where the first summation is over the incoming proton polarizations. These expressions are identical to those 
given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression 
for the spin-averaged squared matrix element. Our result 
contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that 
our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.

The pn process contain four diagrams analogous to the the diagrams for the pp process (there are only four, of course, 
because the neutrons cannot radiate the $A'$). The new diagram that is relevant in the pn process is shown in 
Fig.~\ref{fig:npdiagram} and yields a contribution of 
%
\begin{widetext}
\begin{equation}
M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \varepsilon.
\end{equation}
\end{widetext}
%
The pn processes likewise yield a squared amplitude, 
$\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
the full expression here.

%-------------- NP Feynman Diagram
\begin{figure}
\includegraphics[width=8cm]{npdiagram.pdf}
\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
pp diagram shown in Fig.~\ref{fig:ppdiagram}.}
\label{fig:npdiagram}
\end{figure}

@@

The quantity of interest is the rate of energy emission through dark gauge bosons. 
From the spin-summed, squared amplitudes described in the previous subsection, 
the energy emission rate is obtained by integrating over the phase space, 
and adding a factor of the energy of the emitted particle. To be specific, the 
energy emission rate per unit volume is 
%
\begin{widetext}
\beq
\label{eq:rate1}
Q_i = (2\pi)^4 \int\, E_{\mathrm{A}'} \, \sum_{s_1,s_2}\, \vert \mathcal{M}_i \vert^2 f(p_1) f(p_2)\delta^{(4)}(p_1+p_2-p_3-p_4-\qa)\, \dd \Pi,
\eeq
\end{widetext}
%
where 
%
\begin{equation}
d\Pi = \frac{\dd^3 \vec{q}_{\mathrm{A}'}}{(2\pi)^3 2E_{\mathrm{A}'}}\, \prod_{i=1}^{4}\, \frac{\dd^3 \vec{p}_i}{(2\pi^3) 2E_1}
\end{equation} 
is the Lorentz-invariant phase space interval, 
$ E_{\mathrm{A}'}$ is the energy of the emitted $A'$ boson, 
$f(p)$ are the phase-space densities of the incoming nucleons, and 
the index $i$ refers to either the pp or pn processes. 
The nucleons in the core are comfortably non-degenerate and non-relativistic, 
so the Pauli blocking factor is omitted from Eq.~(\ref{eq:rate1}) and we take 
all nucleons to have a Maxwell-Boltzmann momentum distribution, so 
\beq
f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_N T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_N T} \right).
\eeq
%
We chose a baryon number density of $n_{\mathrm{b}} \approx 1.8 \times 10^{38}\, \mathrm{cm}^{-3}$ and a 
core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
I can probably find something in the literature, but please put something here if you have a citation.}

@@

To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
we assumed that $A'$ production takes place in a stellar core of radius $\sim 1$~km, so that 
the total luminosity of $A'$ is 
%
\begin{equation}
L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}})
\end{equation}
%
where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$, 
so that writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$ and 
$L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
%
\begin{equation}
\label{eq:bound1}
\varepsilon \lesssim \sqrt{\frac{L_{\nu}}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
\end{equation}
%
Following SOMEBODY \arz{We need a citation here.}, we derive a constraint taking 
$L_{\nu} \approx 10^{53}\, \mathrm{erg/s} \approx 4 \times 10^{37}\, \mathrm{MeV}^2$.

The constraint derived in this manner from Eq.~(\ref{eq:bound1}) sets the lower limit on the 
exclusion band shown in Figure~\ref{fig:bound1}, which we will discuss in more detail 
below. If all of the $A'$ produced in the core left the supernova freely, the bound of values of 
$\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. However, 
as we have already mentioned, $\varepsilon$ can become sufficiently large that only a negligible 
amount of energy actually leaves the supernova core because of either $A'$ decays or scattering. 
These considerations place an upper limit on the values of $\varepsilon$ for which this constraint 
applies, and we discuss these effects in the next two subsections.

@@

The constraint from the streaming limit above provides an upper bound on the allowed coupling 
(or lower bound on the excluded coupling) from the production on $A'$ bosons. 
In order to function as an effective cooling channel, enough of the dark gauge bosons 
must escape the supernova. As the coupling increases, so do processes that prevent this escape, 
and so the excluded region has an upper bound, above which the luminosity again drops below the 
neutrino luminosity. The first such limit may be found by considering decay of the dark bosons 
into Standard Model particles. Standard model particles will scatter and thermalize 
on a timescale much shorter than the timescale for the evolution of the core, so decays 
contribute nothing to the cooling.

The dark boson has a typical lifetime of 
\arz{Cameron, try to rephrase this. This is not the lifetime, but rather the 
mean distance to a decay.}
%
\beq
l = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
\eeq
and so the fraction escaping the supernova before decaying is given by 
\beq
e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \varepsilon^2/(3 E_A)}.
\eeq
%
To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space 
integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds 
as in the previous subsection. The limit is derived in the same way, 
with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. 
The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.

>>>>

As we mentioned above, we find SN1987A constraints on dark photon SIDM models that are considerably different 
from those of \cite{dent_etal12}. If correct, our result has important consequences. 
The Snowmass white paper by Kaplinghat, Tulin, and Yu \cite{kaplinghat_etal13_whitepaper} nicely 
summarizes a variety of constraints on dark electromagnetism models of SIDM. 
One point that is clear from Ref.~\cite{kaplinghat_etal13_whitepaper} is that there exists 
only a narrow range of viable photon mixing parameters that can lead to production of SIDM in the early universe and 
interesting effects on cosmological structure formation, while simultaneously evading all constraints, 
including the constraint of Ref.~\cite{dent_etal12}. Our results suggest that the SN1987A constraints from 
Ref.~\cite{dent_etal12} are too restrictive. The constraints that we quote reveal a region of unrestricted mixing 
parameters that ranges over two orders of magnitude. Interestingly, the parameter space opened by our updated 
constraints corresponds to SIDM models that may have a significant impact on cosmological structure formation, 
particularly the structures of dark matter halos and galaxies.

The discrepancy between our result and that of Ref.~\cite{dent_etal12} arises due to multiple factors. First, it is straightforward to 
demonstrate that the kinematical relationships in given in Appendix A of Ref.~\cite{dent_etal12} are incorrect. Second, the 
squared matrix elements given in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} are incorrect. Our squared matrix elements 
are considerably more complicated. Multiple errors must have led to the incorrect squared matrix elements in 
Ref.~\cite{dent_etal12}. At the very least, these errors include simplification using the incorrect kinematics and neglect of the 
mass of the gauge boson (which, while legitimate for the $\sim$meV-mass axion, is not justified in this context). 
Discrepancies in addition to those kinematical issues must also be present, 
the causes of which are not apparent from the exposition, because the squared matrix 
elements in Eq.~(A3) and Eq.~(C18) of Ref.~\cite{dent_etal12} do not obey the 
correct symmetries under interchange of the incoming or outgoing baryon momenta. 
Given these errors, we suggest that our results should supercede these previously-published constraints.

@@

\subsection{Brehmsstrahlung of $A'$ Bosons}

@@

\arz{Cameron, can you double check this? I think there were some errors in the momenta and in the relative 
signs of the diagrams. I tried to fix them. Please go over this carefully.}
The eight diagrams contribute the following eight terms to the pp amplitude, 
%
\begin{widetext}
\begin{eqnarray}
	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\ 
	\bar{u}(p_4) \gamma_5 u(p_2)\  \bar{u}(p_3) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed \epsilon  u(p_1), \\
	M_2 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_1}\  
	\bar{u}(p_3) \gamma_5 u(p_2)\  \bar{u}(p_4) \gamma_5 (\slashed{p}_1 - \qa +M_N)\slashed{\epsilon} u(p_1),\\
	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_4 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 - 2 \qa \cdot p_2}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \gamma_5 (\slashed{p}_2 - \qa +M_N)\slashed \epsilon  u(p_2), \\
	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\
	\bar{u}(p_3) \gamma_5 u(p_1)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
	M_6 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_3}\ 
	\bar{u}(p_4) \gamma_5 u(p_1)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_3 + \qa +M_N)\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{k^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_4) \gamma_5 u(p_2)\ \bar{u}(p_3) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),\\
	M_8 &=& -\frac{4 M_N}{ m_\pi} \frac{f_{\mathrm{pp}}^2\, e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{m_{A^\prime}^2 + 2 \qa \cdot p_4}\ 
	\bar{u}(p_3) \gamma_5 u(p_2)\ \bar{u}(p_4) \slashed{\epsilon} (\slashed{p}_4 + \qa +M_N)\gamma_5 u(p_1),
\end{eqnarray}
\end{widetext}
%
where the dark photon polarization is given by $\epsilon^{\nu}$. The squared amplitude is given by 
%
\begin{equation}
\vert \mathcal{M}_{\mathrm{pp}} \vert^2 = \sum_{s_1,s_2}\, \left\vert \sum_{i=1}^{8}\, M_i \right\vert^2, 
\end{equation}
%
where the first summation is over the incoming proton polarizations. These expressions are identical to those 
given in Ref.~\cite{dent_etal12}; however, they do not simplify significantly if the correct kinematics are used. 
Unfortunately, with the kinematical relations above, the squared amplitude does not yield a tidy expression 
for the spin-averaged squared matrix element. Our result 
contains over 200 terms, so we do not reproduce it here for reasons of convenience. However, we note that 
our result for $\vert \mathcal{M}_{\mathrm{pp}} \vert^2$ is symmetric under exchange of $k$ and $l$ as required.

The pn process contain four diagrams analogous to the the diagrams for the pp process (there are only four, of course, 
because the neutrons cannot radiate the $A'$). The new diagram that is relevant in the pn process is shown in 
Fig.~\ref{fig:npdiagram} and yields a contribution of 
%
\begin{widetext}
\begin{equation}
M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e\, \varepsilon}{l^2-m_\pi^2}  \frac{1}{(l-\qa)^2 - m_\pi^2} 
\bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p_4) \gamma_5 u(p_2) (\qa - 2l)\cdot \varepsilon.
\end{equation}
\end{widetext}
%
The pn processes likewise yield a squared amplitude, 
$\vert \mathcal{M}_{\mathrm{pn}} \vert^2$ that is unwieldy, so we do not give the 
the full expression here.

%-------------- NP Feynman Diagram
\begin{figure}
\includegraphics[width=8cm]{npdiagram.pdf}
\caption{One of the five Feynman diagrams for the np process. This particular diagram shows 
internal brehmsstrahlung off of the charged pion. The remaining four diagrams are analogous to the 
pp diagram shown in Fig.~\ref{fig:ppdiagram}. In the case of the np processes, there are only four 
diagrams for brehmsstrahlung off of the external legs because two of the legs correspond to the 
uncharged neutron.}
\label{fig:npdiagram}
\end{figure}

@@

The quantity of interest is the rate of energy emission through dark gauge bosons. 
From the spin-summed, squared amplitudes described in the previous subsection, 
the energy emission rate is obtained by integrating over the phase space, 
and adding a factor of the energy of the emitted particle. To be specific, the 
energy emission rate per unit volume is 
%
\begin{widetext}
\beq
\label{eq:rate1}
Q_i = (2\pi)^4 \int\, E_{\mathrm{A}'} \, \sum_{s_1,s_2}\, \vert \mathcal{M}_i \vert^2 f(p_1) f(p_2)\delta^{(4)}(p_1+p_2-p_3-p_4-\qa)\, \dd \Pi,
\eeq
\end{widetext}
%
where 
%
\begin{equation}
d\Pi = \frac{\dd^3 \vec{q}_{\mathrm{A}'}}{(2\pi)^3 2E_{\mathrm{A}'}}\, \prod_{i=1}^{4}\, \frac{\dd^3 \vec{p}_i}{(2\pi^3) 2E_1}
\end{equation} 
is the Lorentz-invariant phase space interval, 
$ E_{\mathrm{A}'}$ is the energy of the emitted $A'$ boson, 
$f(p)$ are the phase-space densities of the incoming nucleons, and 
the index $i$ refers to either the pp or pn processes. 
The nucleons in the core are comfortably non-degenerate and non-relativistic, 
so the Pauli blocking factor is omitted from Eq.~(\ref{eq:rate1}) and we take 
all nucleons to have a Maxwell-Boltzmann phase-space distribution distribution, 
\beq
f(p) =  \frac{n_b}{2} \left( \frac{2 \pi}{M_N T} \right)^{3/2} \exp \left(-\frac{p^2}{2 M_N T} \right).
\eeq
%
We choose a baryon number density of $n_{\mathrm{b}} \approx 1.8 \times 10^{38}\, \mathrm{cm}^{-3}$ and a 
core supernova temperature of $T = 30\, \mathrm{MeV}$, both of which are typical choices and thought to 
be representative of supernova cores. \arz{Need to put a citation here for the properties of supernova cores. 
I can probably find something in the literature, but please put something here if you have a citation.}

@@

To obtain the dark gauge boson luminosity from $Q_{\mathrm{pp}}$ and $Q_{\mathrm{pn}}$, 
we assumed that $A'$ production takes place in a stellar core of radius $\sim 1$~km, so that 
the total luminosity of $A'$ is 
%
\begin{equation}
L_{\mathrm{A}'} = V (Q_{\mathrm{pp}} + Q_{\mathrm{pn}})
\end{equation}
%
where $V$ is the volume of the sphere. Clearly, $L_{\mathrm{A}'}$ is proportional to $\varepsilon^2$. 
Writing $L_{\mathrm{A}'} = \varepsilon^2 I_{\mathrm{A}'}(m_{\mathrm{A}'},T)$, as in Ref.~\cite{dent_etal12}, 
and $L_{\nu}$ as the neutrino luminosity, we can write the constraint as 
%
\begin{equation}
\label{eq:bound1}
\varepsilon \lesssim \sqrt{\frac{L_{\nu}}{I_{\mathrm{A}'}(m_{\mathrm{A}'}, T)}}.
\end{equation}
%
Following SOMEBODY \arz{We need a citation here.}, we derive a constraint taking 
$L_{\nu} \approx 10^{53}\, \mathrm{erg/s} \approx 4 \times 10^{37}\, \mathrm{MeV}^2$.

The constraint derived in this manner from Eq.~(\ref{eq:bound1}) sets the lower limit on the 
exclusion band shown in Figure~\ref{fig:constraint}. We will discuss Fig.~\ref{fig:constraint} 
in more detail below. If all of the $A'$ produced in the core leave the supernova freely, all 
values of $\varepsilon$ higher than those given by Eq.~(\ref{eq:bound1}) would be ruled out. 
However, as we have already mentioned, $\varepsilon$ can become sufficiently large that only a 
negligible amount of energy actually exits the supernova core. For large values or $\varepsilon$, 
this can occur because of either $A'$ decays or $A'$ scattering. These additional considerations place 
an upper limit on the values of $\varepsilon$ for which this constraint applies, 
and we discuss these effects in the next two subsections.

@@

The constraint from the streaming limit above provides an upper bound on the allowed coupling 
from the production on $A'$ bosons. In order to function as an effective cooling channel, the 
radiated dark gauge bosons must escape the supernova in sufficient numbers. 
As the coupling increases, so do processes that prevent this escape, 
and so the excluded region has an upper bound, above which the luminosity again drops below the 
neutrino luminosity. The first such limit may be found by considering decay of the dark bosons 
into Standard Model particles. Standard model particles will scatter and thermalize 
on a timescale much shorter than the timescale for the evolution of the core, so decays 
contribute nothing to the cooling.

\arz{I removed reference to $N_{\rm eff}$ because for us $N_{\rm eff}=1$ (doesn't it? the 
only kinematically-allowed decay is to electron-positron pairs, correct?). I also rephrased a 
little bit. Please review this. 
The dark boson has a typical lifetime of
\begin{equation}
\tau_{\mathrm{A}'} = \frac{3}{\varepsilon^2 \alpha m_{\mathrm{A}'}},
\end{equation}
where $\alpha$ is the fine structure constant. Therefore, in the relativistic limit, 
the typical travel distance to decay is given by 
%
\beq
l = \gamma \tau_{\mathrm{A}'} = \frac{3 E_{A}}{N_{eff} m_A^2 \varepsilon^2},
\eeq
and so the fraction escaping the supernova before decaying may be estimated as (e.g., \Ref.~\cite{bjorken_etal09})
\beq
e^{r_{decay}/l} = e^{r_{decay} N_{eff} m_A^2 \varepsilon^2/(3 E_A)}.
\eeq
%
To account for the suppression of gauge boson luminosity due to decays we simply multiply the phase space 
integrand in Eq.~(\ref{eq:rate1}) by the exponential suppression factor, after which the calculation proceeds 
as in the previous subsection. The limit is derived in the same way, 
with the additional complication that $I_{\mathrm{A}'}$ is now a function of $\varepsilon $, in addition to $m_{\mathrm{A}'}$ and $T$. 
The constraint Eq.~(\ref{eq:bound1}), therefore, becomes a transcendental equation that must be solved numerically.
